On the Functionality of the Multilayer Perceptron

### 2020-09-23 Thesis/Sections/TheNerualNetwork.tex
Updates to NueralNetwork Thesis Section

\paragraph*{}To quantify the difference between the model's prediction,m $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $\mathbb{J}(y^*,y)$, to the network \cite{Goodfellow,James}.The cost function, also called a \textit{loss} or \textit{objective} function, compares the neural networks output, $y^*$ and the expected output $y$. It returns a single value, usually a floating-point number which measures the \textit{poorness} of the prediction. A high cost value indicates a \textit{poor} prediction, and a low cost indicates a reasonable prediction.

\paragraph*{}$\mathbb{J}(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}. For this $k$-classes classification task, we choose to use a \textit{Categorical Crossentropy} (CXE) cost function. For a single predictions sample, it is defined \cite{Goodfellow}:
\begin{equation}
\label{eqn-CategoricalCrossentropy}
\text{CXE}\big[ y^* , y \big] = - \sum_{i=0}^{k-1} y^*_i \log_{10}(y_i) 
\end{equation}
In practice, this operation is performed over a batch of samples and an average is computed and used a \textit{batch loss} \cite{Goodfellow}.

@@

\paragraph*{}For this project, we employ an \textit{Adaptive-Moments} optimization algorithm, also called \textit{ADAM} for short. It is a powerful variant of algorithms with an adaptive learning rate. It tracks an exponentially decaying average of past gradients, as well as exponentially decaying average of past squared gradients \cite{Geron}. As an extra step, ADAM also includes correction factors for both first order moments, and uses a combination of them to update the network parameters \cite{Geron,Goodfellow}. For a given iteration $(i)$, The ADAM update is given:
\begin{equation}
\label{eqn-ADAMupdate}
\begin{split}
s^{(i)} &= \rho_1 s^{(i-1)} + (1 - \rho_1) \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]  \\
r^{(i)} &= \rho_2 r^{(i-1)} + (1 - \rho_2) \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big] \odot
							\frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]  \\
s'^{(i)} &= \frac{s^{(i)}}{1-\rho_1^t} \\
r'^{(i)} &= \frac{r^{(i)}}{1-\rho_2^t} \\
\Theta^{(i)} &= \Theta^{(i-1)} + (-\alpha)\frac{s'^{(i)}}{\sqrt{r'^{(i)}}+\delta} \\
\end{split}
\end{equation}

>>>>

\paragraph*{}To quantify the difference between the model's prediction, $y^*$ and the expected output, $y$, we introduce a \textit{cost function}, $J(y^*,y)$, to the network \cite{Goodfellow,James}. The cost function, also called a \textit{loss} or \textit{objective} function, compares the neural networks output, $y^*$ and the expected output $y$. It returns a single value, usually a floating-point number which measures the \textit{poorness} of the prediction. A high cost value indicates a \textit{poor} prediction, and a low cost indicates a reasonable prediction.

\paragraph*{}$J(y^*,y)$ can take many forms and is often dependent on particular task or data set provided \cite{James}. For this $k$-classes classification task, we choose to use a \textit{Categorical Crossentropy} (CXE) cost function. For a single predictions sample, it is defined \cite{Goodfellow}:
\begin{equation}
\label{eqn-CategoricalCrossentropy}
\text{CXE}\big[ y^* , y \big] = - \sum_{i=0}^{k-1} y^*_i \log_{10}(y_i) 
\end{equation}
In practice, this operation is performed over a batch of samples and an average is computed and used a \textit{batch loss} \cite{Goodfellow}.

@@

\paragraph*{}For this project, we employ an \textit{Adaptive-Moments} optimization algorithm, also called \textit{ADAM} for short. It is a powerful variant of algorithms with an adaptive learning rate. It tracks an exponentially decaying average of past gradients, as well as exponentially decaying average of past squared gradients \cite{Geron}. This produces a far more aggressive optimizer at a higher computational cost. For a given iteration $(i)$, The ADAM update is given:
\begin{equation}
\label{eqn-ADAMupdate}
\begin{split}
s^{(i)} &= \rho_1 s^{(i-1)} + (1 - \rho_1) \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]  \\
r^{(i)} &= \rho_2 r^{(i-1)} + (1 - \rho_2) \frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big] \odot
							\frac{1}{m} \nabla_{\Theta} \Big[\sum_{n=1}^{m} J(y^{*(n)},y^{(n)}) \Big]  \\
s'^{(i)} &= \frac{s^{(i)}}{1-\rho_1^t} \\
r'^{(i)} &= \frac{r^{(i)}}{1-\rho_2^t} \\
\Theta^{(i)} &= \Theta^{(i-1)} + (-\alpha)\frac{s'^{(i)}}{\sqrt{r'^{(i)}}+\delta} \\
\end{split}
\end{equation}
